{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-10-24 main.tex
First_Draft

\documentclass[11pt,twoside,a4paper]{article}
\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

	\subsection{Draft-Overview}
	\begin{itemize}
		\item Introduce the concept of random functions
		\item Introduce the concept of square integrable deterministic \& random functions
		\item Explain basis expansions (so basis of the vector space $L^2$ and b-spline basis as an example) 
		\item Motivate Karhunen-Loeve-Expansion and Eigenbasis from PCA		
		\item Explain Scalar-on-Function Regression
		\item Estimation through basis-expansion (incl. Eigenbasis) and estimation with roughness penalty
		\item Address approximation error due to basis-truncation
	\end{itemize}

	\subsection{Literature}
	\begin{itemize}
		\item \cite{kokoszka_introduction_2017}
		\item \cite{hsing_theoretical_2015}
		\item \cite{ramsay_functional_2005}
		\item \cite{horvath_inference_2012}
	\end{itemize}

@@

	\subsection{Draft-Overview}
	\begin{itemize}
		\item Motivate Simulation for some data generating process from application
		\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
		\item Present Results
		\item Explain relevance for application
	\end{itemize}

	\subsection{Literature}
	\begin{itemize}
		\item \cite{shonkwiler_explorations_2009}
	\end{itemize}

@@

	\subsection{Draft-Overview}
	\begin{itemize}
		\item 
	\end{itemize}

	\subsection{Literature}
	\begin{itemize}
		\item 
	\end{itemize}

>>>>

\documentclass[11pt,twoside,a4paper]{article}
\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

	\subsection{Draft-Overview}
	\begin{itemize}
		\item Introduce the concept of random functions
		\item Introduce the concept of square integrable deterministic \& random functions
		\item Explain basis expansions (so basis of the vector space $L^2$ and b-spline basis as an example) 
		\item Motivate Karhunen-Loeve-Expansion and Eigenbasis from PCA		
		\item Explain Scalar-on-Function Regression
		\item Estimation through basis-expansion (incl. Eigenbasis) [and estimation with roughness penalty]
		\item Address approximation error due to basis-truncation
	\end{itemize}

	\subsection{Literature}
	\begin{itemize}
		\item \cite{kokoszka_introduction_2017}
		\item \cite{hsing_theoretical_2015}
		\item \cite{ramsay_functional_2005}
		\item \cite{horvath_inference_2012}
		\item \cite{cai_prediction_2006}
		\item \cite{levitin_introduction_2007}
	\end{itemize}

@@

	\subsection{Draft-Overview}
	\begin{itemize}
		\item Motivate Simulation for some data generating process from application
		\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
		\item Prediction not Inference
		\item Present Results
		\item Explain relevance for application
	\end{itemize}

	\subsection{Literature}
	\begin{itemize}
		\item \cite{shonkwiler_explorations_2009}
		\item R-packages: fda, refund, mgcv
	\end{itemize}

@@

	\subsection{Draft-Overview}
	\begin{itemize}
		\item Prediction not Inference
		\item IID data set (no dependence between the curves, don't want to do functional time series)
		\item Not necessarily data from economics (like biology, sports, whatever)
		\item Smooth curves or random walk (both fine)
		\item \href{https://functionaldata.wordpress.ncsu.edu/resources/}{https://functionaldata.wordpress.ncsu.edu/resources/}
	\end{itemize}

	\subsection{Literature}
	\begin{itemize}
		\item \cite{carey_life_2002}
	\end{itemize}

	\section{Outlook}

	\subsection{Literature}
	\begin{itemize}
		\item \cite{James.2009} (shape-restrictions)
	\end{itemize}
